Verifying Demonstrations

### 2019-02-13 paper/protest-model.tex
Minor reformulations in protest model

\emph{Formalizing the notion of crowd estimation.} 
Each participant who wants to be counted must submit a \emph{participation proof}.
The proof must be associated with the protest (\ie its cause identifier \(cid\)), and its time and location must coincide with one of the subprotests.

@@

The strength function \(\str\) can be used to regulate the trust in the 
participation count estimated. In general, \(\str\) can be defined as a 
weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
weights \(\omega_i\) being the trust in the witness corresponding to that proof 
share \(s_i\), and the threshold \(\theta\) represents the total trust needed 
to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being valid if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

>>>>

%\emph{Formalizing the notion of crowd estimation.} 
Each participant who wants to be counted must submit a \emph{participation proof}.
The proof must be associated with the protest (\ie its cause identifier \(cid\)), and its time and location must coincide with one of the subprotests.

@@

The strength function \(\str\) can be used to regulate the trust in the 
estimated participation count.
In general, \(\str\) can be defined as a weighted sum of the proof shares, 
\(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) being the trust in 
the witness corresponding to the proof share \(s_i\), and the threshold 
\(\theta\) represents the total trust needed to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called 
\emph{trusted witness}, participating in the protest. For instance, the role of 
the trusted witness could be taken by the independent journalist Jane.
In this situation, the weights would be 1 for trusted witnesses and 
0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being valid if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.
